### 2014-09-11 paper/paper.Rmd
moved another section with maps up
labels for truancy adjusted

@@

# 2. Teachers, computers, and libraries at school make a difference in math scores

@@

@@

# 3. Starting school at an older age generates lower average math scores.

```{r agemaps, fig.width=12, fig.height=7, echo = FALSE, message = FALSE, warning = FALSE}
# Extract map polygons for modern world
world <- getMap(resolution = "low")
library(plyr)
world.polys <- extractPolygons(world)
detach("package:plyr")

student2012.sub.agemedian$medianstart <- factor(student2012.sub.agemedian$medianstart)
student2012.sub.map <- left_join(student2012.sub.agemedian, world.polys)
ggplot(data=world.polys) + geom_path(aes(x=X1, y=X2, order=order, group=group), colour=I("grey90")) + 
  geom_polygon(data=student2012.sub.map, aes(x=X1, y=X2, order=order, group=group, fill=medianstart)) +
  scale_fill_discrete("Median Start Age") +
  new_theme_empty + theme(legend.position="bottom")
#ggsave("agestartmap.pdf", width=12, height=7)
```

@@

#studentLuke$name <- as.character(studentLuke$CNT)
# unique(anti_join(studentLuke.sub, world.polys)[1])
#studentLuke$name[studentLuke$name=="United Arab Emirates"] <- "UAE"
#studentLuke$name[studentLuke$name=="United Kingdom"] <- "UK"
#studentLuke$name[studentLuke$name=="Serbia"] <- "Serbia"
#studentLuke$name[studentLuke$name=="Korea"] <- "South Korea"
#studentLuke$name[studentLuke$name=="Chinese Taipei"] <- "Taiwan"
#studentLuke$name[studentLuke$name=="Slovak Republic"] <- "Slovakia"
#studentLuke$name[studentLuke$name=="Russian Federation"] <- "Russia"
#studentLuke$name[studentLuke$name=="Perm(Russian Federation)"] <- "Russia"
#studentLuke$name[studentLuke$name=="Hong Kong-China"] <- "Hong Kong"
#studentLuke$name[studentLuke$name=="China-Shanghai"] <- "China"
#studentLuke$name[studentLuke$name=="Macau"] <- "China"
#studentLuke$name[studentLuke$name=="Connecticut (USA)"] <- "USA"
#studentLuke$name[studentLuke$name=="Florida (USA)"] <- "USA"
#studentLuke$name[studentLuke$name=="Massachusetts (USA)"] <- "USA"
#studentLuke$name[studentLuke$name=="United States of America"] <- "USA"
unique(studentLuke$name)
studentLuke$name <- factor(studentLuke$name)

@@

```{r clean, echo=FALSE}
#student2012$CNT = student2012$name
student2012$OECD <- as.character(student2012$OECD)
#student2012[student2012$name == "Albania", ]$OECD = "Albania"
student2012$math = as.numeric(student2012[, "PV1MATH"])
student2012$read = as.numeric(student2012[, "PV1READ"])
student2012$sci = as.numeric(student2012[, "PV1SCIE"])

@@

#qplot(x = SC22Q01, y = value, color = variable, facets = ~name, data = truancy.df, group = group, geom = "line") + xlab("Reported Truancy") + ylab("Test Scores") + scale_colour_discrete(name = "Subject", labels=c("Math", "Science", "Reading"))
qplot(x = SC22Q01, y = value, facets = ~name, data = truancy.df, geom = "line", group=name) + xlab("Reported Truancy") + ylab("Math Scores") + theme_bw()
```

>>>>

shorten_countrynames = function(df) {
df$name = as.character(df$name)
df$name[df$name=="Hong Kong S.A.R."] <- "Hong Kong"
df$name[df$name=="Republic of Serbia"] <- "Serbia"
df$name[df$name=="United Arab Emirates"] <- "UAE"
df$name[df$name=="United States of America"] <- "USA"
df$name[df$name=="United Kingdom"] <- "UK"

@@

# 2. Starting school at an older age generates lower average math scores.

```{r agemaps, fig.width=12, fig.height=7, echo = FALSE, message = FALSE, warning = FALSE}
student2012.sub.agemedian$medianstart <- factor(student2012.sub.agemedian$medianstart)
student2012.sub.map <- left_join(student2012.sub.agemedian, world.polys)
ggplot(data=world.polys) + geom_path(aes(x=X1, y=X2, order=order, group=group), colour=I("grey90")) + 
  geom_polygon(data=student2012.sub.map, aes(x=X1, y=X2, order=order, group=group, fill=medianstart)) +
  scale_fill_discrete("Median Start Age") +
  new_theme_empty + theme(legend.position="bottom")
#ggsave("agestartmap.pdf", width=12, height=7)
```

# 3. Teachers, computers, and libraries at school make a difference in math scores

@@

```{r shortencountrynames, warning=FALSE, message=FALSE, echo=FALSE, results='hide'}
#school2012$name <- as.character(school2012$name)
#student2012$name <- as.character(student2012$name)
school2012 = shorten_countrynames(school2012)
student2012 = shorten_countrynames(student2012)
```

@@

@@

#studentLuke$name <- as.character(studentLuke$CNT)
# unique(anti_join(studentLuke.sub, world.polys)[1])
#studentLuke$name[studentLuke$name=="United Arab Emirates"] <- "UAE"
#studentLuke$name[studentLuke$name=="United Kingdom"] <- "UK"
#studentLuke$name[studentLuke$name=="Serbia"] <- "Serbia"
#studentLuke$name[studentLuke$name=="Korea"] <- "South Korea"
#studentLuke$name[studentLuke$name=="Chinese Taipei"] <- "Taiwan"
#studentLuke$name[studentLuke$name=="Slovak Republic"] <- "Slovakia"
#studentLuke$name[studentLuke$name=="Russian Federation"] <- "Russia"
#studentLuke$name[studentLuke$name=="Perm(Russian Federation)"] <- "Russia"
#studentLuke$name[studentLuke$name=="Hong Kong-China"] <- "Hong Kong"
#studentLuke$name[studentLuke$name=="China-Shanghai"] <- "China"
#studentLuke$name[studentLuke$name=="Macau"] <- "China"
#studentLuke$name[studentLuke$name=="Connecticut (USA)"] <- "USA"
#studentLuke$name[studentLuke$name=="Florida (USA)"] <- "USA"
#studentLuke$name[studentLuke$name=="Massachusetts (USA)"] <- "USA"
#studentLuke$name[studentLuke$name=="United States of America"] <- "USA"
#unique(studentLuke$name)
studentLuke$name <- factor(studentLuke$name)

@@

```{r clean, echo=FALSE, message = FALSE, warning = FALSE}
#student2012$CNT = student2012$name
student2012$OECD <- as.character(student2012$OECD)
#student2012[student2012$name == "Albania", ]$OECD = "Albania"
student2012$math = as.numeric(student2012[, "PV1MATH"])
student2012$read = as.numeric(student2012[, "PV1READ"])
student2012$sci = as.numeric(student2012[, "PV1SCIE"])

@@

#qplot(x = SC22Q01, y = value, color = variable, facets = ~name, data = truancy.df, group = group, geom = "line") + xlab("Reported Truancy") + ylab("Test Scores") + scale_colour_discrete(name = "Subject", labels=c("Math", "Science", "Reading"))
qplot(x = SC22Q01, y = value, facets = ~name, data = truancy.df, group=name, geom="smooth", se=F) + 
  scale_x_discrete("Reported Truancy, 0=None, 1=Little, 2=Some, 3=Lot", labels=c("Not"="0", "Little"="1", "Some"="2", "Lot"="3")) + 
  ylab("Math Scores") + theme_bw()
```
